Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-12-18 Articles/Article 1/main.tex
.
ALERT ABOUT BUG
2d platform extensions

\subsection{Optimization Algorithm}

@@

@@

\add{
	- include execution times \\
	- PLOT: kernel on robot graphics \\
}

>>>>

\subsection{Kinematic Control}

@@

\alert{THIS WILL TOTALLY STOP MOVEMENT IN TIGHT SPACES, NEED ADDITIONAL PART. (Maybe use some kind of derivative of Rep Field).}

@@

\add{
	- include execution times \\
	- PLOT: kernel on robot graphics \\
	- IMPORTANT: maybe add 2D mobile platform results \\
}
